---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SASformatR

<!-- badges: start -->
<!-- badges: end -->

The goal of SASformatR is to port the functionality of SAS formats to R, to ease in the creation of data sets.

## Installation

You can install the development version of SASformatR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tomratford/SASformatR")
```

## Example

Like as in SAS, we can create formats uses `proc_format()`.

```{r example}
library(SASformatR)

proc_format(
  PARAMCD = value(
    "SYSBP" = "Systolic Blood Pressure",
    "DIABP" = "Diastolic Blood Pressure",
    "HR" = "Heart Rate"
  ),
  YNn = value(
    `1` = 'Y',
    `2` = 'N'
  )
)
```

These values can be regular enum -> enum formats, or can be numeric ranges if provided in the format below.

```{r cr8_fmt}
proc_format(
  AGEGR1 = value(
    "< 21" = "<21",
    "21 - 39" = "21 - 39",
    "40 <=" = ">=40"
  )
)
```

These values can then be applied to a regular vector using the `SASformat` function.

```{r apply_fmt}
age <- c(10,20,30,40,50)
agegr1 <- SASformat(age, "AGEGR1")
```

When viewed in a data frame these values will appear formatted.
```{r dataframe}
dplyr::bind_cols(age = age, agegr1 = agegr1)
```

for more information, check out `vignette("getting_started", package="SASformatR")`.
