---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SASformatR)
```

`SASformatR` is a port of the [SAS]() style of [formats](). 
Formats are defined in a similar way to SAS.

```{r}
proc_format(
  PARAMCD = value(
    "SYSBP" = "Systolic Blood Pressure",
    "DIABP" = "Diastolic Blood Pressure",
    "HR" = "Heart Rate"
  ),
  PARAMN = invalue(
    "SYSBP" = 1,
    "DIABP" = 2,
    "HP" = 3
  ),
  YNn = value(
    `1` = 'Y',
    `2` = 'N'
  )
)
```

Unlike in SAS - there is no requirement to specify a format as a 'character' format.
Like in SAS, ranges are available to simplify numeric formats.

```{r}
proc_format(
  AGEGR1 = value(
    "< 21" = "<21",
    "21 - 39" = "21 - 39",
    "40 <=" = ">=40"
  )
)
```

the `x1 - x2` format represents a closed interval of $[x1,x2]$.

To add a format a value - apply the `SASformat()` function to a value with the format of choice
```{r}
age <- c(10,20,30,40,50)
agegr1 <- SASformat(age, "AGEGR1")
```

To convert using a format - apply the `put` or `input` function to a value - as you would in SAS.
